---
title: "Circle Buffer Function"
author: "Harun Celik"
date: "2023-07-06"
output: html_document
---

```{r, eval=FALSE}
library(googleway)
library(dplyr)
library(sf)
library(tidycensus)
library(tigris)
library(DSPGGrocery)
library(oce)
library(leaflet)
library(cli)
```

```{r, include=FALSE, eval=FALSE}
set_key(key = Sys.getenv("PLACES_KEY"))
```

# Convert the address of LakeView to a lat/long 
```{r}
df_geocode <- google_geocode(address = "St, Lamoni, IA") %>%
  .$results %>%
  .$geometry %>%
  .$location
```

# Pull the stores in LakeView with the API call
```{r}
df_grocery_all <- google_places(location = c(df_geocode$lat
, df_geocode$lng), 
                                    keyword = "grocery", 
                                    rankby = "distance") %>%
  .$results %>%
  transmute(name, 
            lat = .$geometry$location$lat, 
            lng = .$geometry$location$lng, 
            types,
            vicinity,
            state = strsplit(.$plus_code$compound_code, split = ", ")) %>%
  filter(state != "NANA") %>%
  mutate(state = sapply(.$state, "[[", 2))
  
```

# Change types column from list to just first item
```{r}
for (item in 1:nrow(df_grocery_all)) {
  df_grocery_all$types[item] <- df_grocery_all$types[[item]][1]
}

rm(item)
```

# Filter by the first item in types
```{r}
df_grocery_only <- df_grocery_all %>%
  filter(types == "grocery_or_supermarket")
```

# Start Circling

## Get dataframe of four closest points
```{r}
source(file = "../Alex/Distance_Comparator.R")
source(file = "../Alex/UTM_Zoner.R")
source(file = "../Alex/Distance_Euclidean.R")

df_grocery_circle <- Distance_Comparator(df_grocery_only = df_grocery_only,
                                         df_geocode = df_geocode) %>%
  filter(distance_vector == max(distance_vector))
rm(df_new,
   northeast_dist, 
   northwest_dist,
   southeast_dist,
   southwest_dist)
```

## Create Spatial Objects
```{r}
buffer_point_origin <- st_as_sf(df_geocode, coords = c("lng", "lat"), crs = "NAD83")
store_points <- st_as_sf(df_grocery_all, coords = c("lng", "lat"), crs = "NAD83")
furthest_point <- st_as_sf(df_grocery_circle, coords = c("lng", "lat"), crs = "NAD83")
```

## Origin Point Buffer
```{r}
buffer_circle <- st_buffer(buffer_point_origin, 
                           dist = as.integer(ceiling(st_distance(buffer_point_origin$geometry,
                                                                 furthest_point$geometry))))
```

## Experimental
### Cast Line
```{r, eval=FALSE}
line_coords <- matrix(c(unlist(buffer_point_origin$geometry), 
                        unlist(furthest_point$geometry)), 
                      ncol = 2, 
                      byrow = T)
  
buffer_line <- st_linestring(line_coords) %>%
  st_sfc(crs = 4326)
```

### Take Line Intersect
```{r, eval=FALSE}
trimmed_buffer <- st_intersection(buffer_point$geometry, buffer_line)

## This doesn't produce the expected results, the circle is not cut out by the distance of the line. A better option is just to use the st_distance() function and set that as the argument for the circle buffer.
```

### Visualize SF Objects
```{r, warning=FALSE, eval=FALSE}
plot(buffer_point$geometry, col='blue')
plot(buffer_point_origin$geometry, col='red', add=T)
plot(furthest_point$geometry, col = 'green', add=T)
plot(buffer_line, col='white', add=T)
plot(store_points$geometry, col='white', add=T)
```


# Pull Cities and County
## Pull_Counties function
```{r, eval=FALSE}
#' Takes a List of States and Retreives All Counties in State
#' 
#' @author Harun Celik
#'
#' @description the function takes a list of states and passes them through a loop
#' to pull all counties in the provided states.
#' 
#' @param state_list A list of state values to iterate through. State values should be unique.
#'

Pull_Counties <- function(state_list = unique(df_grocery_all$state)) {
  all_counties <- NULL
  for (index in 1:length(state_list)) {
    county_loop <- counties(state = state_list[index])
    
    Sys.sleep(2)
    
   all_counties <- rbind(all_counties, county_loop)
  }
  
  return(all_counties)
}
```

## Pull_Cities function
```{r, eval=FALSE}
#' Takes a List of States and Retreives All Cities in State
#' 
#' @author Harun Celik
#'
#' @description the function takes a list of states and passes them through a loop
#' to pull all cities in the provided states.
#' 
#' @param state_list A list of state values to iterate through. State values should be unique.
#'

Pull_Cities <- function(state_list = unique(df_grocery_all$state)) {
  all_cities <- NULL
  for (index in 1:length(state_list)) {
    city_loop <- places(state = state_list[index])
    
    Sys.sleep(2)
    
   all_cities <- rbind(all_cities, city_loop)
  }
  
  return(all_cities)
}
```

## Save city and county information
```{r}
all_counties <- Pull_Counties(state_list = unique(df_grocery_all$state))
all_cities <- Pull_Cities(state_list = unique(df_grocery_all$state))
```

## Intersect Buffer with Counties and Cities
```{r, warning=FALSE}
grocery_counties_inter <- st_intersection(all_counties, buffer_circle)
grocery_cities_inter <- st_intersection(all_cities, buffer_circle)
```

## Building argument for census and market size calls
```{r}
df_census_call <- st_join(x = grocery_cities_inter, y = all_counties, join = st_nearest_feature) %>%
  transmute(cities =  NAME.x,
            counties = NAME.y,
            state = STATEFP.x)
```

## Plotting Intersections
```{r, eval=FALSE}
plot(all_counties$geometry)
plot(buffer_circle, col='gray', add=T)
plot(grocery_counties_inter$geometry, add=T)
plot(store_points$geometry, col='red', add=T)
```
# Leaflet Testing
```{r, warning=FALSE, eval=FALSE}
leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  addPolygons(data = all_counties$geometry, 
              fillOpacity = 0.05, 
              fillColor = 'darkred', 
              color = 'black',
              opacity = .5) %>%
  addPolygons(data = buffer_circle$geometry, fillColor = 'gray') %>%
  addPolygons(data = grocery_cities_inter$geometry, fillColor = 'blue') %>%
  addCircleMarkers(lng = df_grocery_all$lng, lat = df_grocery_all$lat, color= 'green', popup = df_grocery_all$name, radius = 10)
  
```

