---
title: "Google Places API Testing"
author: "Harun Celik"
date: "2023-06-21"
output: html_document
---

# Load Library

```{r}
library(googleway)
library(sf)
library(dplyr)
library(ggplot2)
library(leaflet)
library(ggvoronoi)
```

# Add Google Places Key

```{r, include=FALSE}
set_key(key = Sys.getenv("PLACES_KEY"))
```

# Ames Google Places API

## Testing Pull for Ames

```{r}
# Trying to find dollar stores in a 4 mile radius.

ames_dollar_stores <- google_places(search_string = "dollar", location = c(42.034534, -93.620369), radius = 6500, keyword = "store")
```

## Extract Results from API Pul into `results`

```{r}
results <- ames_dollar_stores$results
```

## Wrangle Data to Extract Latitude and Longitude

```{r}
spatial_results <- results %>% 
  transmute(name = name, lat = geometry$location$lat, lng = geometry$location$lng)
```

## Display a Leaflet Map with Markers from `spatial_results`

```{r}
leaflet(spatial_results) %>%
  addProviderTiles("CartoDB.Positron") %>%
  addMarkers(lng = spatial_results$lng, lat = spatial_results$lat, popup = spatial_results$name) %>%
  setView(-98.5795, 39.8282, zoom=3)
```

# Mock Dataset

## Making a Mock Dataset

```{r}
cities <- c("Ames", "Des Moines", "Waterloo", "Chicago")
lat <- c(42.034534, 41.619549, 42.499504, 41.881832)
lng <- c(-93.620369, -93.598022, -92.358665, -87.623177)

test_cities <- data.frame(cities, lat, lng)
```

## Create a Function for Multiple Location Pull

```{r}
places_multiloc_pull <- function(df, name = NULL, 
                                 search_string = NULL, 
                                 keyword = NULL, 
                                 lat = c(df[,2]),
                                 lng = df[,3],
                                 radius = 6500, 
                                 type = NULL, 
                                 api_key = Sys.getenv("PLACES_KEY"), 
                                 place_type = NULL) {
  
  result_list <- list()
  
  for (i in 1:dim(test_cities)[1]) {
    
    start_time <- Sys.time()
    
    string <- sprintf("df_%f", i)
    
    spring <- noquote(string) 
    
    spring <- googleway::google_places(search_string = search_string, 
                                   name = name, 
                                   location = c(lat[i], lng[i]), 
                                   radius = radius, 
                                   keyword = keyword, 
                                   key = api_key)
    
    
    Sys.sleep(2)
    
    result_list <- append(result_list, list(spring$results))
    
    end_time <- Sys.time()
    total_time <- end_time - start_time
    print(sprintf("Execution time for iteration %d is %.2f", i, total_time))
  }
  
  return(result_list)
  
}
```

## Use `places_multiloc_pull()` with Mock Dataset 

```{r}
all_list <- places_multiloc_pull(df = test_cities, search_string = "dollar")
```

## Flatten the Data for Saving as RDS 

```{r, eval=FAlSE}
combined_df_new <- bind_rows(all_list[[1]], 
                             all_list[[2]], 
                             all_list[[3]], 
                             all_list[[4]]) %>%
  tidyr::unnest(cols = c(geometry, 
                         opening_hours, 
                         photos, 
                         plus_code))


#'*The following saves the data frame as an RDS.*
## saveRDS(object = combined_df_new, file = "Google_Places_DollarStores.rds")
```


