
|---
title: "Spatial Testing"
author: "Harun Celik"
date: "2023-06-26"
output: html_document
---


```{r}
library(googleway)
library(dplyr)
library(sf)
library(ggplot2)
library(tidycensus)
library(tigris)
library(leaflet)
```

```{r, include=FALSE}
set_key(key = Sys.getenv("PLACES_KEY"))
```

# Convert the address of LakeView to a lat/long 
```{r}
df_geocode <- google_geocode(address = "23 Main St, Lake View, IA, United States, Iowa") %>%
  .$results %>%
  .$geometry %>%
  .$location
```

# Pull the stores in LakeView with the API call
```{r}
df_grocery <- google_places(location = c(df_geocode$lat
, df_geocode$lng), 
                                    keyword = "grocery", 
                                    rankby = "distance") %>%
  .$results %>%
  transmute(name, 
            lat = .$geometry$location$lat, 
            lng = .$geometry$location$lng, 
            types,
            vicinity)
```

# Turn store locations into an sf object
## Making a polygon method one
```{r}
# Make a list of lng and lat
sf_grocery_polygon <- cbind(df_grocery$lng, df_grocery$lat)

# Close shape and make polygon
sf_grocery_polygon <- rbind(sf_grocery_polygon, sf_grocery_polygon[1, ]) %>%
  list() %>%
  st_polygon()
```

## Making a polygon method two
```{r}
sf_grocery_polygon_union <- st_as_sf(df_grocery, coords = c("lng", "lat"), crs = 4326) %>%
  summarise(geometry = st_union(geometry)) %>%
  st_cast("POLYGON")
```

## Making store points
```{r}
sf_grocery_points <- st_as_sf(df_grocery, coords = c("lng", "lat"))
```

## Creating a bounding box from points
```{r}
sf_bounds <- st_bbox(sf_grocery_points) %>% 
  st_as_sfc()
```

```{r}
sf_hull <- df_grocery %>%
  select(lng, lat) %>%
  st_as_sf(coords = c("lng", "lat")) %>%
  st_union() %>%
  st_convex_hull()
```

# Plotting Different Polygon Types
```{r, warning=FALSE, eval=FALSE}
plot(ia)
plot(ia_counties, add=TRUE)
#plot(sf_bounds, col='purple', add=TRUE)
plot(sf_hull, col='darkgreen', add=TRUE)
#plot(sf_grocery_polygon, col='green', add=TRUE)
#plot(sf_grocery_polygon_union, col='blue', add=TRUE)
#plot(sf_grocery_points, col='white', add=TRUE)
```


# Finding Cities and Counties
## Loading Jay's Functions
```{r}
## Loading Jay's Functions

get_county <- function(x) {
  #input: a single-row data frame, columns 1, 2 = lon, lat
  #                                column 3 = state name
  #output: x with extra column for county name
  counties <- counties(state=x[["state"]])
  
  point <- st_as_sf(x, coords = c("lon", "lat"), crs=st_crs(counties))
  
  point %>%
    st_join(counties, join=st_intersects) %>%
    mutate(county = NAME) %>%
    select(county) %>%
    st_drop_geometry() -> county

    return(cbind(x, county) )
}


get_city <- function(x) {
  # input: a single-row data frame, columns 1, 2 = lon, lat
  #                                column 3 = state name
  # (does not require county column)
  # output: x with extra column for city name

  cities <- places(state=x[["state"]])
  
  point <- st_as_sf(x, coords = c("lon", "lat"), crs=st_crs(cities))
  
  point %>%
    st_join(cities, join=st_intersects) %>%
    mutate(city = NAME) %>%
    select(city) %>%
    st_drop_geometry() -> city
  
  return(cbind(x, city) )
}



get_cities_in_county <- function(x) {
  #input: a single-row data frame, a column named "state"
  #                                a column named "county"
  #output: x with extra column for all the cities w/in a county
  
  state <- x[["state"]]
  county <- x[["county"]]
  
  # Get TIGER/Line geometry for all the counties and cities/places
  # in our state of interest
  cities <- places(state=state)
  counties <- counties(state=state)
  
  counties %>% 
    filter(NAME == county) %>% 
    st_join(cities, join=st_intersects) %>% 
    pull(NAME.y) %>% 
    sort() %>% 
    paste(collapse = ", ") -> city_list
  
  return(cbind(x, city_list))
  
} 
```

## Load IA towns and Provide Population Cut Off
```{r}
ia_towns <- get_decennial(geography = "place",
                          state="Iowa",
                          variables  = "DP1_0001C",
                          sumfile = "dp",
                          output = "wide",
                          geometry = TRUE,
                          cb=FALSE,
                          keep_geo_vars = TRUE
)

pop_cutoff <- 500

big_towns <- ia_towns %>% filter(DP1_0001C>=pop_cutoff)
```

## Iowa Variables
```{r}
ia_counties <- counties(state = "Iowa")
```

## Intersecting Polygon with Cities
```{r}
sf_hull <- st_sf(sf_hull, crs = st_crs(ia_counties))

poly_counties <- sf_hull %>%
  st_intersection(ia_counties)

poly_cities <- sf_hull %>%
  st_intersection(big_towns)
```

## Plotting Intersections 
```{r, eval=FALSE}
plot(ia)
plot(st_geometry(ia_counties), col='beige', add = TRUE)
plot(st_geometry(poly_counties), col = 'lightblue', add=TRUE)
plot(st_geometry(poly_cities), col = 'lightgreen', add = TRUE)
```

## Leflet Testing

```{r, warning=FALSE}
leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  addPolygons(data = poly_counties, 
              fillOpacity = 0.05, 
              fillColor = 'darkred', 
              color = 'black',
              opacity = .5) %>%
  addPolygons(data = poly_cities, fillColor = 'blue', popup = poly_cities$NAME.x) %>%
  addCircleMarkers(lng = df_grocery$lng, lat = df_grocery$lat, color= 'green', popup = df_grocery$name, radius = 10)
```

# Test
```{r}
Grocery_Store_Map()
```

```{r}
leaflet() %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  addPolygons(data = StoreInfo$grocery_counties_inter, 
              fillOpacity = 0.05, 
              fillColor = 'darkred', 
              color = 'black',
              opacity = .5) %>%
  addPolygons(data = StoreInfo$grocery_cities_inter, fillColor = 'blue', popup = StoreInfo$grocery_cities_inter$NAME.x) %>%
  addCircleMarkers(lng = StoreInfo$df_grocery$lng, lat = StoreInfo$df_grocery$lat, color= 'green', popup = StoreInfo$df_grocery$name, radius = 10)
```




















