---
title: "Estimating Expenses"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Estimating Expenses}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(DSPGGrocery)
```

One essential element of the calculation for store profitability is the estimation for the various expenses that a potential owner might have to contend with when they open their store. This tool allows for users to test the profitability of different budgetary percentages of various expense categories for grocery stores to help determine the resources necessary for a store to succeed in a given area.

## Bizminer/Vertical IQ Percentages

Many of the functions used in this package utilize percentages taken from both Bizminer and Vertical IQ, two financial analysis and market research firms, as defaults in their calculations. These percentages are based off of industry 3-year averages for grocery stores as of 2022 and the average between the two firms is taken for all of the specified items of expense below. The slider inputs are automatically set to these average percentages when displayed.

Functions that use Bizminer/Vertical IQ percentages as defaults:

-   `Gross_Margin()`

-   `Cost_of_Goods_Sold()`

-   `Employee_Wages()`

-   `Officer_Compensation()`

-   `Other_Operating_Expense()`

-   `Other_Income()`

-   `Interest_Income()`

## Categories of Expenses

Five different categories of expenses are accounted for in this tool:

### Cost of Goods Sold

This represents how much of the total estimated revenue is spent on the cost of goods (inventory). The calculation for this item takes the total estimated revenue and the selected gross margin percentage into account.

Associated Functions:

-   `Gross_Margin()`

-   `Cost_of_Goods_Sold()`

### Operating Expenses

Comprises expenses such as compensation for company officers, employee wages and other common operating expenses of grocery stores. Users can select percentages for each of these expenses or they can rely on the default value provided by Bizminer.

Associated Functions:

-   `Employee_Wages()`

-   `Officer_Compensation()`

-   `Other_Operating_Expense()`

### Asset Depreciation

Covers the annual loss from the depreciation of various assets required to own and operate a grocery store. The value of a list of assets are divided by their associated use life to determine the annual lost in value from asset depreciation. The tool gives the user the option to fill out a form for one of two scenarios: one if the user plans to own a building and the other if the user plans to rent.

Associated Functions:

-   `Depreciation_1()`

-   `Depreciation_2()`

### Loan Interest

Covers the annual interest on a user-specified loan (if a loan was taken out). The annual cost of interest on a loan is calculated from the loan amount and its annual interest rate, entered by the user.

Associated Function:

-   `Interest_Expense()`

### Rent (if leasing building)

This covers the annual cost of rent for a leased building. Users can enter their monthly rate of rent

to determine the annual cost of rent for their building.

Associated Function:

-   `Annual_Rent()`

## Secondary Sources of Income

Another important factor to consider is secondary sources of income. These are broken up into two main categories:

### Income from interest

Income collected from interest-bearing assets.

Associated Function:

-   `Interest_Income()`

### Other Income

This could include special services outside the revenue from sold goods alone, such as special grocery delivery services or membership fees for discount clubs, among other things.

Associated Function:

-   `Other_Income()`

## Pre-Tax Profit

In the tool, the estimated expenses will be subtracted from the total estimated revenue and the estimated secondary income will then be added in the calculation for the estimated pre-tax profit . Users will be able to adjust the percentages to suite their individual needs and determine profitability taking both expenses and market size into account.
